Forecasting the US Election 2024

### 2024-11-04 paper/paper.qmd
add survey

Include a link to your Google Forms survey here. Survey Link Copy of the Survey Questions

# Additional data details

>>>>

https://forms.gle/d1pLxx5UNsC9x63s9

```{r,echo=FALSE}
knitr::include_graphics("survey/1.png")
knitr::include_graphics("survey/2.png")
knitr::include_graphics("survey/3.png")
knitr::include_graphics("survey/4.png")
knitr::include_graphics("survey/5.png")
knitr::include_graphics("survey/6.png")
knitr::include_graphics("survey/7.png")
knitr::include_graphics("survey/8.png")
knitr::include_graphics("survey/9.png")
knitr::include_graphics("survey/10.png")

```
# Additional data details
